Embedding Dimension of Polyhedral Losses

### 2020-01-31 colt-20/embed-dim.tex
proof of prop 10

  $(\impliedby)$
  \bo{This one needs a bit of work.}
  If the intersection graph forms a path, then each level set has at most two neighbors.
  The level sets are convex polytopes, as they form a power diagram\dots.

  As each path has a source, take the corresponding report to be $r_1$, and proceed in order through the path to enumerate the ordering.
  As the property is well-defined on the simplex, the boundaries of the level sets cannot intersect on $\relint(\simplex)$ without adding an edge.
  Combining this fact with the fact that level sets of finite elicitable properties are convex polytopes (and therefore defined as the intersection of a finite number of halfspaces), the level set boundaries must be hyperplanes intersected with $\simplex$. 
\end{proof}

>>>>

  $(\impliedby)$
  \bo{Done with my pass. Not very happy with it but good enough I hope.}
  If the intersection graph forms a path, then we can enumerate the vertices from source to sink as $r_1,\ldots,r_{|\R|}$.
  The level sets are full-dimensional (in the simplex) convex polytopes whose intersections only occur in the relative boundary, as they form cells of a power diagram.
  Since $\gamma_{r_1}$ intersects only with $\gamma_{r_2}$ on the relative interior of the simplex, and both sets are convex, this intersection must be a hyperplane intersecting the simplex.
  (Otherwise, one of the sets would not be convex, or $\gamma_{r_1}$ would intersect with some other level set on the relative interior.
  We can now ``delete'' $\gamma_{r_1}$, more formally, consider the convex polytope $\gamma_{r_2} \cup \ldots \cup \gamma_{r_{|\R|}}$.
  The same argument now applies to $\gamma_{r_2}$, giving that it is intersects with $\gamma_{r_3}$ along a hyperplane intersected with the simplex; and so on.
%
%  As each path has a source, take the corresponding report to be $r_1$, and proceed in order through the path to enumerate the ordering.
%  As the property is well-defined on the simplex, the boundaries of the level sets cannot intersect on $\relint(\simplex)$ without adding an edge.
%  Combining this fact with the fact that level sets of finite elicitable properties are convex polytopes (and therefore defined as the intersection of a finite number of halfspaces), the level set boundaries must be hyperplanes intersected with $\simplex$. 
\end{proof}
